\documentclass[class=NCU_thesis, crop=false]{standalone}
\begin{document}

\chapter{The ATLAS detector}
\section{Coordinates}
	The ATLAS (\textbf{A} \textbf{T}oroidal \textbf{L}HC \textbf{A}pparatu\textbf{S}) experiment is one of the seven detector in Large Hadron Collider (LHC) at CERN (European Organization for Nuclear Research). Its cylindrical symmetry and end caps covers nearly $4\pi$ in solid angle.
	
	A coordinate system is used to describe every recorded signals nearby. The origin is set at the center of the detector, or the interaction point (IP). The x-axis points toward the center of the LHC ring; the y-axis points vertically upward; the z-axis points along one of the beam pipe direction such that a right-handed coordinate sysetem is created.
	
	A modified version of cylindrical coordinate is more commonly used in the experiment. The pseudorapidity $\eta \equiv -\ln\tan(\theta / 2)$, in which $\theta$ is the polar angle in cylindrical coordinate, is used to decribe the angle between the z-axis and the direction of interest. $(r, \phi)$ is the same system to describe the tranverse plane, with $\phi$ being the azimuthal angle. In addition, the cone size is defined as $\Delta R \equiv \sqrt{(\Delta \phi)^2 + (\Delta \eta)^2}$.

\section{Components of ATLAS}
	Depending its function, the components are categorized into four parts - inner detector, calorimeters, muon spectrometer, and the magnetic system. Each of them consist of smaller layers.
	
	\subsection{Inner Detector}
		Beginning few centimeters from the IP, the inner decector's main function is to track the trace of charged particles by their interations with the materials. A 2T magnetic field, which surrounds the whole inner detector, causes the charged ones to bend. Based on the directions and the curvatures, one can determine their charges and momenta preliminarily. The inner detector comprises three parts - the pixel detector, the semi-conductor tracker (SCT), and the transition rediation tracker (TRT).
		
		Located at the innermost part, the pixel detector contains four layers of modules, which is made up of 250 $\mu$m-thick silicon, each is 2 centimeters by 6 centimeters in size in the direction perpendicular to the beam. Three disks, which are made up of similar material, are at each end cap of the detector. Each module includes about 47,000 pixels, measuring 50 by 400 $\mu$m each. It covers pseudorapidity range $\lvert \eta \rvert < 2.5$ and its proximity to the IP is meant to measure extremely precise trace of the charged particles.
		
		The semi-conductor tracker, having a similar concept and function to the pixel detector, lies in the middle part of the inner detector. Although having a resemblance to the pixel detector, the SCT is in a long and narrow strip-shape rather than small pixels and covers the perpendicular directions to the beam instead of nearly full coverage. The SCT, which overlays a larger area than the pixel detector does, has more sampled points and thus is of great importance on tracking the transverse directions with roughly the same accuracy compared to the pixel detector.
		
		The outermost component, TRT, includes straw tube trackers and transition radiation detectors. Though its precision in tracking is not high and its coverage in pseudorapidity, about $\rvert \eta \lvert < 2.0$, is not wide compared to the other two components, TRT possesses transition radiation detection capability, which is useful for identifying charged particles. Since the lighter particles tend to have higher speed, which generates greater transition radiation, electrons and positrons, the lightest charged particles, would leave strong signals in TRT.
	
	\subsection{Calorimeters}
		Outside the solenoidal magnet, which envelops the inner detector, are the calorimeters. By absorbing the particles, the calorimeters measure the energies of them. Two layers of components compose the calorimeter systems, the inner electromagnetic (EM) calorimeter and the outer hadronic calorimeter.
		
		As its name suggests, the EM calorimeter absorbs energies from particles that interact electromagnetically, including photons and charged particles. A pseudorapidity of range $\lvert \eta \rvert < 3.2$ is covered by high-granularity lead/liquid argon(LAr) EM calorimeter, which includes the barrel and end cap. In addition, a LAr persampler which is meant to correct the energy loss in materials of the calorimeters covers $\lvert \eta \rvert < 1.8$. For the forward region, which has the range $3.1 < \lvert \eta \rvert < 4.9$, a LAr EM calorimeter with copper is also deployed.
		
		Hadronic calorimeter, although it is less precise in both energies magnitude and localization, absorbs energies from the particles that interact via strong force. Steel/scintillator-tile covering $\lvert \eta \rvert < 1.7$, two copper/LAr end cap calorimeters overlaying $1.5 < \lvert \eta \rvert < 3.2$, and a forward-regional ($3.1 < \lvert \eta \rvert < 4.9$) tungsten absorbers constitute the hadronic calorimeter.
	
	\subsection{Muon Spectrometer}

\end{document}